---
title: Typst template for MNB
subtitle: Almost like latex!
format: mnbhundred-typst
author:
    - name: Marcell Granát
      affiliations: Economist
place: 18 November, 2024
knitr:
    opts_chunk: 
        echo: false
        eval: true
        collapse: true
        dev: "svg"
        comment: "#>"
        fig.height: 6
        fig.width: 14
        fig.align: "center"
bibliography: references.bib
---

```{r}
#| warning: false
#| message: false
source("_extensions/mnbhundred/tables.R")
```

```{=typst}
#let emph = (fill: rgb("9a2515"), it) => text(fill: fill, weight:"bold", it)
```

# Section Slide as Header Level 1

## Slide Title as Header Level 2

Next, we'll brief review some theme-specific components.

-   Note that *all* of the standard Quarto + Typst [features](https://quarto.org/docs/output-formats/typst.html) can be used with this theme
-   Also, all the [Touying](https://touying-typ.github.io) features can be used by **Typst native code**
-   Insert citation: @abe2010

## Additional Theme Classes

### Some extra things you can do with the mnbhundred theme

Special classes for emphasis

-   `.alert` class for default emphasis, e.g. [the second accent color]{.fg}
-   `.fg` class for custom color, e.g. [with `options='fill: rgb("#5D639E")'`]{.fg options="fill: rgb(\"#5D639E\")"}.
-   `.bg` class for custom **background**, e.g. [with the default color]{.bg}.

Cross-references

-   `.button` class provides a Beamer-like button, e.g. [[Demo]{.button}](#sec-demo)

## Summary {#sec-summary}

### A Minimalistic Presentation Theme for Quarto + Typst with Touying

Add the theme to an existing project

``` bash
quarto install extension marcellgranat/quarto-mnbhundred-typst
```

... or, create a new project using this slide deck as a lean template

``` bash
quarto use template marcellgranat/quarto-mnbhundred-typst
```

... or just copy the `_extension` folder.

## columns


```{r}
#| echo: true
library(tidyverse)
```

```{=typst}
#set page(columns: 2)
```
```{r}
#| fig-cap: Cars randomly
ggplot(data = iris) + 
    geom_point(aes(Sepal.Length, Sepal.Width)) + 
    theme(
        plot.background = element_blank()
    )
```

### Longer Demo {#sec-demo}


For a more comprehensive demo, see the [demo slides](https://kazuyanagimoto.com/quarto-slides-typst/slides/quarto-mnbhundred-typst/mnbhundred.pdf) and [code](https://github.com/kazuyanagimoto/quarto-slides-typst/blob/main/slides/quarto-mnbhundred-typst/mnbhundred.qmd)!



## Examples on full page

One TODO is still here.

```{=typst}
#set page(columns: 1)
```

```{r}
#| cap: Cars randomly
ggplot(data = iris) + 
    geom_point(aes(Sepal.Length, Sepal.Width)) + 
    custom_theme -
    .gg_finalise
```

```{r}
#| cap: "**Random szöveg**"
#| comment: "nem minden érték helyes.."
iris |> 
    head(10) |> 
    gt::gt() |> 
    .gt_finalise()
```

## References